Generalized Tractability

### 2023-04-10 GeneralizedTractability_230310.tex
Updates from Overleaf

\begin{definition}
	A problem is sub-$h \circ T$ tractable if
	\begin{equation*}
		\lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{h(cT(\varepsilon^{-1},d,\vp))} = 0 \qquad \forall c>0
	\end{equation*}
\end{definition}

@@

\noindent \textbf{Necessary Condition:}\\
Suppose that the problem is  sub-$h \circ T$ tractable. Then, for any $c>0$ there exists a positive integer $V_c$ such that  
\[
	\comp(\varepsilon,d)\le 
	\left\lfloor{h(cT(\varepsilon^{-1},d)) \right\rfloor \qquad \forall \varepsilon^{-1} + d \ge V_c.
\]
By the definition of complexity in \eqref{eq:comp_def}, it follows that 
\[
	\lambda_{n(\varepsilon,d,c),d} \le \varepsilon \quad \forall \varepsilon^{-1} + d \ge V_c, \qquad \text{where }
	n(\varepsilon,d,c):=\left\lfloor{h(cT(\varepsilon^{-1},d)) \right\rfloor.
\]
Since $h(cT(\cdot,d))$ is non-decreasing, it follows that
\begin{equation*}
		n(\varepsilon,d,c)\le  h(cT(\varepsilon^{-1},d)) \le  h(cT(\lambda^{-1}_{n(\varepsilon,d,c),d},d)) \qquad  \quad \forall \varepsilon^{-1} + d \ge V_c.
\end{equation*}

@@

Consequently,
\begin{align*}
\lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{ h(2cT(\varepsilon^{-1},d))  }
& \le \lim_{\varepsilon^{-1} + d \to \infty} \frac{ \left\lceil 
	S_c \, h(cT(\varepsilon^{-1},d)) \right\rceil}{ [h(cT(\varepsilon^{-1},d))]^2  } \qquad \text{by \eqref{eq:h_cond}}
\\
& \le \lim_{\varepsilon^{-1} + d \to \infty} \frac{
	S_c \, h(cT(\varepsilon^{-1},d))+1}{ [h(cT(\varepsilon^{-1},d))]^2  }  \\
& = \lim_{\varepsilon^{-1} + d \to \infty} \left \{\frac{
	S_c }{ h(cT(\varepsilon^{-1},d))  }  + \frac{
	1}{ [h(cT(\varepsilon^{-1},d))]^2 } \right \} \\
& = 0, \qquad \text{since } \lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d) = \infty.
\end{align*}	
\fred{Maybe this last assumption on $T$ tending to infinity also depends on the additivity or something similar.}

>>>>

\begin{definition} \label{def:subhT}
	A problem is sub-$h \circ T$ tractable if
	\begin{equation*}
		\lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{h(cT(\varepsilon^{-1},d,\vp))} = 0 \qquad \forall c>0
	\end{equation*}
\end{definition}

@@

Consequently,
\begin{align*}
\lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{ h(2cT(\varepsilon^{-1},d))  }
& \le \lim_{\varepsilon^{-1} + d \to \infty} \frac{ \left\lceil 
	S_c \, h(cT(\varepsilon^{-1},d)) \right\rceil}{ [h(cT(\varepsilon^{-1},d))]^2  } \qquad \text{by \eqref{eq:h_cond}}
\\
& \le \lim_{\varepsilon^{-1} + d \to \infty} \frac{
	S_c \, h(cT(\varepsilon^{-1},d))+1}{ [h(cT(\varepsilon^{-1},d))]^2  }  \\
& = \lim_{\varepsilon^{-1} + d \to \infty} \left \{\frac{
	S_c }{ h(cT(\varepsilon^{-1},d))  }  + \frac{
	1}{ [h(cT(\varepsilon^{-1},d))]^2 } \right \} \\
& = 0, \qquad \text{since } \lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d) = \infty.
\end{align*}	
\fred{Maybe this last assumption on $T$ tending to infinity also depends on the additivity or something similar.}  Since $c$ is arbitrary, we have satisfied the condition of Definition \ref{def:subhT}.

\noindent \textbf{Necessary Condition:}\\
Suppose that the problem is  sub-$h \circ T$ tractable. Then, for any $c>0$ there exists a positive integer $V_c$ such that  
\[
	\comp(\varepsilon,d)\le 
	\left\lfloor h(cT(\varepsilon^{-1},d)) \right\rfloor \qquad \forall \varepsilon^{-1} + d \ge V_c.
\]
By the definition of complexity in \eqref{eq:comp_def}, it follows that 
\[
	\lambda_{n(\varepsilon,d,c),d} \le \varepsilon \quad \forall \varepsilon^{-1} + d \ge V_c, \qquad \text{where }
	n(\varepsilon,d,c):=\left\lfloor h(cT(\varepsilon^{-1},d)) \right\rfloor.
\]
Since $h(cT(\cdot,d))$ is non-decreasing, it follows that
\begin{equation*}
		n(\varepsilon,d,c)\le  h(cT(\varepsilon^{-1},d)) \le  h(cT(\lambda^{-1}_{n(\varepsilon,d,c),d},d)) \qquad  \quad \forall \varepsilon^{-1} + d \ge V_c.
\end{equation*}

@@
